Colonies - Compute Continuums across Platforms

### 2023-04-03 paper_2023/paper.tex
wip

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{\textit{arXiv} Template}

@@

Argo is a ...

@@

The serverless workflow project \cite{serverlessworkflow} aims at providing a vendor-neutral workflow DSL. Synapse is a workflow management system implementing the serverless workflow specification. It is important to point out that Colonies does not provide an infrastructure for function execution. Instead, Colonies primary role is to serve as a platform for coordinating function executions, which are carried out by distributed executor services.

Colonies is based on a microservice architecture. J. Represa et al. \cite{GarciaRepresa1740746} discusses various challenges developing microservice-based workflow management for industrial automation. They concludes that microservice-based workflow technologies is feasible for industrial usage, especially considering its flexibility. The main contribution of this paper is a technica

SCAFE: A Service-Centered Cloud-Native Workflow Engine Architecture

https://www.alibabacloud.com/product/serverless-workflow
https://serverlessworkflow.io/

https://github.com/serverlessworkflow/synapse

AWS Step Functions to design and run a serverless workflow that coordinates multiple AWS Lambda functions.

@@

Integrating Raft with the Colonies framework allows incoming assign requests to be directed towards the leading Colonies server, thereby ensuring that only one Colonies server replica handles such requests. Figure \ref{fig:ha_deployment} shows an overview of a high-availability Colonies deployment. A new leader is elected in the event that a Colonies server replica fails. The Raft protocol also enables seamless updates to the Colonies server software by making it possible to upgrade each replica individually. As a result, Colonies becomes well-suited for Kubernetes deployments.

>>>>

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{Technical Report}
\renewcommand{\undertitle}{Technical Report}
%\renewcommand{\shorttitle}{\textit{arXiv} Template}

@@

Argo \cite{argowf} is an open source container-native workflow engine for orchestrating parallel jobs on Kubernetes. It is can be used for running CI/CD pipelines or compute intensive machine learning or data processing tasks where each job runs as a container. In contrast, Colonies offers a more versatile approach, allowing jobs to be launched within a container. As launching new containers on Kubernetes can occasionally be time-consuming, Colonies can delivers higher throughput as the costs of starting new jobs are minimal. This is particular useful when launching large container images, or workloads (e.g. Julia scripts) or that takes relative long time to start.

@@

The serverless workflow project \cite{serverlessworkflows} aims at providing a vendor-neutral workflow DSL. Synapse \cite{synapse} is a workflow management system similar to Argo, but that implements the serverless workflow specification. A similar engine is proposed in \cite{scafe}. It is important to point out that Colonies does not provide an infrastructure for function execution. Instead, Colonies primary role is to serve as a platform for coordinating function executions, which are carried out by distributed executor.

J. Represa et al. \cite{GarciaRepresa1740746} explore various challenges associated with developing microservice-based workflow management for industrial automation within the context of the Arrowhead project. The authors conclude that microservice-based workflow technologies is viable for industrial applications, particularly due to their inherent flexibility. The primary contribution of this paper is a comprehensive technical description of how to implement a distributed workflow engine based on microservice principles, extending beyond orchestrating microservices to execute automation tasks.

@@

Incorporting Raft with the Colonies framework allows incoming assign requests to be directed towards the leading Colonies server, thereby ensuring that only one Colonies server replica handles such requests. Figure \ref{fig:ha_deployment} shows an overview of a high-availability Colonies deployment. A new leader is elected in the event that a Colonies server replica fails. The Raft protocol also enables seamless updates to the Colonies server software by making it possible to upgrade each replica individually. As a result, Colonies becomes well-suited for Kubernetes deployments.
